A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-16 Paper.tex
Cleaning up .bib (slight issue)
Fixing issue with the reference section by making changes to the .bib
However... there is a strange issue where if authors have similar names and appear close in the reference section their name gets replaced with a ------. Not sure if this is intended by IEEEtrans style or not.

Link to someone that wanted to change this: https://tex.stackexchange.com/questions/29381/is-it-normal-for-bibtex-to-replace-similar-author-names-with
Cleaned up Abstract

	%The end of the abstract, I think, needs a better explanation of the survey other than stating that RO-SLAM techniques will be explored, ie: a more unifying theme
	\begin{abstract}		
		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM). In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders. Sensing these landmarks provide the robot with information such as range and bearing to the landmark, which are used in various algorithms responsible for determining the robot's pose and the landmark locations within the map. However, some applications have the restriction of using landmarks which are only capable of providing range information, such as wireless and acoustic beacons. Attempting to simultaneously localize and map with this restriction is termed Range-Only Simultaneous Localization and Mapping (RO-SLAM). This paper examines recent advances in the algorithms and technologies utilized to accomplish RO-SLAM.

@@

		  	%Ehhhhh.. This section... I dunno if this section is necissary
			A unique implementation of an underwater acoustic beacons is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}. These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates. The distance between an robot and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon. A localization implementation using these beacons was accomplished by \cite{Erol2008}.

@@

	\section{Conclusion}
	\label{conclusion}
	This paper has introduced the motivation and practicality of RO-SLAM approaches. The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms. The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.

	Given the maturity of SLAM as a research field, the area of RO-SLAM still has lots of area to explore. Most of the common methodologies presented here focus on adapting traditional SLAM algorithms to accommodate only range data. While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with uniques solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.

>>>>

	%The end of the abstract, I think, needs a better explanation of the survey other than stating that RO-SLAM techniques will be explored, ie: a more unifying theme
	\begin{abstract}		
		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM). In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders. Sensing these landmarks provide the robot with information such as range and bearing to the landmark, which are used in various algorithms responsible for determining the robot's pose and the landmark locations within the map. However, some applications have the restriction of using sensors which are only capable of providing range information, such as wireless and acoustic beacons. While these sensors solve the issues associated with distinguishing individual landmarks, they are incapable of providing the robot's relative orientation. Attempting to simultaneously localize and map with this restriction is termed Range-Only Simultaneous Localization and Mapping (RO-SLAM). This paper exams the common range only sensor types, the challenges associated with initializing range only sensors as landmarks, and the filtering techniques used to create the map and localize the robot and beacons.

@@

		  	%Ehhhhh.. This section... I dunno if this section is necessary
			A unique implementation of an underwater acoustic beacons is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}. These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates. The distance between an robot and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon. A localization implementation using these beacons was accomplished by \cite{Erol2008}.

@@

	\section{Conclusion}
	\label{conclusion}
	This paper has introduced the motivation and practicality of RO-SLAM approaches. The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms. The variety of SLAM algorithms as they apply to range-only sensor data are examined here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.

	Given the maturity of SLAM as a research field, the area of RO-SLAM still has lots of area to explore. Most of the common methodologies presented here focus on adapting traditional SLAM algorithms to accommodate only range data. While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with unique solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.
